Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Add summary time-series figure

@@

```{r fig-biome-timeseries, fig.cap = biome_ts_cap, fig.dim = c(10, 8)}
biome_ts_cap <- paste(
  "Overall parameter uncertainty of Hector simulations with permafrost biome."
)
readd(ts_biome_sims)
```

@@

>>>>

```{r fig-summary-ts, fig.cap = summary_ts_cap}
summary_ts_cap <- paste(
  htmlfig(),
  "Mean and 95% confidence interval on Hector simulations ",
  "with different model structures and parameter combinations."
)
fig("ts-summary.png")
```

`r mdcap(summary_ts_cap)`

@@

@@

```{r fig-biome-timeseries, fig.cap = biome_ts_cap, fig.dim = c(10, 8)}
biome_ts_cap <- paste(
  htmlfig(),
  "Overall parameter uncertainty of Hector simulations with permafrost biome."
)
readd(ts_biome_sims)
```
